Holomorphic field theories and higher algebra

### 2022-09-20 draft.tex
partway through explaining invariant theory

\begin{dfn}
A {\em holomorphic QCD theory} with $N$ {\em colors} and $F$ {\em flavors} is the holomorphic field theory on $\CC^2$ where
\begin{itemize}
\item the gauge fields are those of holomorphic BF theory valued in $\sl(N)$, whose fields are
\[
A \in \Omega^{0,\bu}(\CC^2 , \sl(N))[1] \quad\text{and}\quad B \in \Omega^{2,\bu}(\CC^2, \sl(N)^*);
\]
\item the ``quarks'' are fields of a holomorphic $\beta\gamma$ system valued in 
\[
V_Q = \Hom(\CC^F, \underline{N}) \cong \underline{N}^{\oplus F},
\] 
whose fields are
\[
Q \in \Omega^{0,\bu}(\CC^2 , V_Q) \quad\text{and}\quad R \in \Omega^{2,\bu}(\CC^2 , V_Q^*)[1];
\]
\item the ``antiquarks'' are fields of a holomorphic $\beta\gamma$ system valued in the dual representation 
\[
V^*_Q \cong \Hom(\underline{N}, \CC^F) \cong (\underline{N}^*)^{\oplus F}, 
\]
whose fields are
\[
q \in \Omega^{0,\bu}(\CC^2 , V^*_Q) \quad\text{and}\quad r \in \Omega^{2,\bu}(\CC^2 , V_Q) [1].
\]
\end{itemize}

@@

The {\em electric theory} is the holomorphic QCD with $N$ colors and $F$ flavors, {\em without} mesons.
We denote it by~$\cT_{\sfE}(F, N)$.

The {\em magnetic theory} is the holomorphic QCD with $\check{N}$ colors and $F$ flavors, but with mesons $\check{M}$ where $$V_{\check{M}} = \End(\CC^F) \cong \CC^{\oplus F^2}$$ and with superpotential $$\check{W} =  \Tr(\check{q} \check{M}  \check{Q}),$$
where we compose the linear maps before tracing over~$V_{\check{N}}$.
We denote this theory by~$\cT_{\sfM}(F, \check{N})$.
\end{dfn}

@@

@@

For the holomorphic QCD theory $\cT(F,N)$ without mesons, 
the moduli stack of classical vacua is 
\[
\cM_{\rm vac} \cong T^*[1] \left(V_Q \oplus V_Q^*)/SL(N)\right).
\]
By contrast the moduli space is a well-known variety, 
\[
M_{\rm vac}(\cT) \cong \Gr(F, N),
\]
the affine cone of a Grassmannian \owen{under Pl\"ucker embedding? need to check.} 
This result follows from classical invariant theory.
(The quark part of a vacuum lies on an $SL(N)$-orbit of $V_Q$, which consists of $F$ copies of the fundamental representation $\CC^N$, and likewise for the antiquark part.
Identifying the $SL(N)$-invariant functions on $V_Q \oplus V^*_Q$ is one of the fundamental theorems of classical invariant theory.)
The moduli space for the magnetic theory is a bit more complicated but follows from invariant theory as well.

>>>>

\begin{dfn}
A {\em holomorphic QCD theory} with $N$ {\em colors} and $F$ {\em flavors} is the holomorphic field theory on $\CC^2$ where
\begin{itemize}
\item the gauge fields are those of holomorphic BF theory valued in $\sl(N)$, whose fields are
\[
A \in \Omega^{0,\bu}(\CC^2 , \sl(N))[1] \quad\text{and}\quad B \in \Omega^{2,\bu}(\CC^2, \sl(N)^*);
\]
\item the ``quarks'' are fields of a holomorphic $\beta\gamma$ system valued in 
\[
V_Q = \Hom(\CC^F, \underline{N}) \cong \underline{N}^{\oplus F} \cong \CC^{NF},
\] 
whose fields are
\[
Q \in \Omega^{0,\bu}(\CC^2 , V_Q) \quad\text{and}\quad R \in \Omega^{2,\bu}(\CC^2 , V_Q^*)[1];
\]
\item the ``antiquarks'' are fields of a holomorphic $\beta\gamma$ system valued in the dual representation 
\[
V^*_Q \cong \Hom(\underline{N}, \CC^F) \cong (\underline{N}^*)^{\oplus F} \cong \CC^{NF}, 
\]
whose fields are
\[
Q^\dag \in \Omega^{0,\bu}(\CC^2 , V^*_Q) \quad\text{and}\quad R^\dag \in \Omega^{2,\bu}(\CC^2 , V_Q) [1].
\]
\end{itemize}
(The superscript $\dag$ does not mean we apply an operation to $Q$ or $R$; 
it is simply to remind us that these fields are the ``antiparticles''.)

@@

The {\em electric theory} is the holomorphic QCD with $N$ colors and $F$ flavors, {\em without} mesons.
We denote it by~$\cT_{\sfE}(F, N)$.
We use $A, B, Q, R, Q^\dag$, and $R^\dag$ for the fields.

The {\em magnetic theory} $\cT_{\sfM}(F, \check{N})$ is the holomorphic QCD with $\check{N}$ colors and $F$ flavors, but with mesons $\check{M}$ where $$V_{\check{M}} = \End(\CC^F) \cong \CC^{\oplus F^2}$$
(and $\check{L}$ for the partner field to $\check{M}$).
We use $\check{A}, \check{B}, \check{Q}, \check{R}, \check{Q}^\dag$, and $\check{R}^\dag$ for the other fields.
The superpotential is $$\check{W} =  \Tr(\check{Q}^\dag \check{M}  \check{Q}),$$
where we compose the linear maps before tracing over~$V_{\check{N}}$.
\end{dfn}

@@

This claim should seem rather surprising.
In many ways these theories look, on their face, like very different theories:
the gauge groups $SL(N)$ and $SL(\check{N})$ are (usually) different, and
one side has mesons and the other does not.
But this feature also makes the conjecture powerful.

@@

For the holomorphic QCD theory $\cT(F,N)$ without mesons, 
the moduli stack of classical vacua is 
\[
\cM_{\rm vac} \cong T^*[1] \left(V_Q \oplus V_Q^*)/SL(N)\right).
\]
By contrast the moduli space is a variety already well-studied in classical algebraic geometry.
The quark part of a vacuum lies on an $SL(N)$-orbit of $V_Q $, which consists of $F$ copies of the fundamental representation $\CC^N$, and likewise for the antiquark part.

\[
M_{\rm vac}(\cT) \cong ,
\]
the affine cone of a Grassmannian \owen{under Pl\"ucker embedding? need to check.} 
This result follows from classical invariant theory.
(
Identifying the $SL(N)$-invariant functions on $V_Q \oplus V^*_Q$ is one of the fundamental theorems of classical invariant theory.)
The moduli space for the magnetic theory is a bit more complicated but follows from invariant theory as well.
